Improved Global Routing By Using A Star Algorithm

### 2020-06-01 paper.tex
Final paper

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{pgfplots}
\usepackage{subfigure}

@@

\title{Improved Global Routing By Using A Star Algorithm\\}

@@

@@

    \foreach \x in {0,0.5,...,3.5}{
        \foreach \y in {0,0.5,...,2}
            \node[box] at (\x,\y){};
    }
    \node [box,fill=orange] at (0.5,1){S};
    \node[box,fill=orange  ] at (3,1){D};
    \node [box,fill=orange] at (0.5,1.5){};  
    \node [box,fill=orange] at (1,1.5){};  
    \node [box,fill=orange] at (1.5,1.5){};
    \node [box,fill=orange] at (2,1.5){};
    \node [box,fill=orange] at (2.5,1.5){};
    \node [box,fill=orange] at (3,1.5){};
    \node [box,fill=cyan] at (0,1){};
    \node [box,fill=cyan] at (1,1){};
    \node [box,fill=cyan] at (1.5,1){};
    \node[box,fill=black  ] at (2,1){ };  
    \end{tikzpicture}
}
\caption{Comparison between Dijkstra \& A-Star }
\label{fig:GlobalRoutingProcess}
\end{figure}
\medskip
In the illustrative example the visited nodes are marked in cyan color, the path is in orange color, and the blocked cells are black.
Both have path of six cells which in our case they have optimal wire length but totally different running time as Dijkstra visits much more nodes than A-Star
, in the case of many target nodes, Dijkstra might be better in total wire length but much slower than A-Star, with an appropriate heuristic function we can minimize the time and try to reach optimal wire length. The heuristic function is a way of informing the search about the path to a target that provides an intelligent way of guessing which neighbor of the node is going to lead to the target faster. Hence, our heuristic function composed of Manhattan distance, layer index, and some constants.

\begin{multline*}
    h = \ln ((\mid p1 \cdot x-p2 \cdot x\mid+\mid p1 \cdot y-p2 \cdot y\mid)*const1) \\ 
     +(\mid p1 \cdot layerid-p2 \cdot layerid\mid)*const2 \\
\end{multline*}
The global router is implemented using C++ with the boost library, and a parser for LEF/DEF formats. We conducted our experiment with the same configuration and tried to test the global router behavior using A-Star algorithm instead of Dijkstra's.

@@

\subsection{Proposed Algorithm}
% \floatstyle{norules}
\restylefloat{algorithm}
\begin{algorithm}[H]
    \caption{A-Star Algorithm}
    \hspace*{\algorithmicindent} \textbf{Input:} Grid values $g$, Source $s$, Destination $d$\\
    \hspace*{\algorithmicindent} \textbf{Output:} Path\\
    \begin{algorithmic}[1]
    \Procedure {A-Star}{}
    % Return  Average waiting time, throughput
    \Statex Declaration and Initialisation:
    \State Cells $\theta$ % The Cells in the grid.
    \State Visited Nodes $\phi$ % Nodes already visited.
    \State Openlist Nodes $\delta$ % Nodes still to be visited. pq
    \State The cost from Starting point to a given node $g$
    \State The heuristic function $h$
    \State (The cost of $g$ + The cost of $h$) is $f$
    \If{$s$ or $d$ is invalid}
        \Return
    \EndIf
    \If{$s$ or $d$ is blocked}
        \Return
    \EndIf
    \If{$s$ = $d$}
        \Return
    \EndIf
    \State Initialize $\delta$ 
    \State Initialize $\phi$
        \While{$\delta$ is not empty}
            \State $currNode$  = node with least $f$ in $\delta$
            \State $\delta$.Remove($currNode$)
            \State Generate 4 neighbours of $currNode$
            \For{$neighbour \in neighbours$}
            \If{$neighbour$ = $d$}
                \State Get path
                \Return
            \ElsIf{$neighbour \notin \phi$ and $neighbour$ is not blocked}
                \State $gnew$ = $currNode$.$g$ + distance between neighbour and currNode
                \State $hnew$ = distance from $d$ to $neighbour$
                \State $fnew$ = $gnew$ + $hnew$
                \If{$fnew < neighbour$.$f$}
                \State $neighbour$.$g$ = $currNode$.$g$ + distance between neighbour and currNode
                \State $neighbour$.$h$ = distance from $d$ to $neighbour$
                \State $neighbour$.$f$ = $neighbour$.$g$ + $neighbour$.$h$
                \State $\delta$.Add($neighbour$)
                \EndIf
            \EndIf
            \EndFor
        \State $\phi$.Add($currNode$)
        \EndWhile
        \EndProcedure
    \end{algorithmic}
\end{algorithm}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ASSUMPTIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Assumptions}

The proposed scheduling algorithm is software simulated using a Python script which simulates scheduling independent CPU-bound processes on a single processor environment which guarantees that no more than a single process is getting scheduled at any arbitrary moment. Each process is assumed to have its own predetermined burst time, arrival time and the queue to which each one belongs. The proposed approach is non-preemptive. For the sake of giving an example, if a process was lately introduced to a queue denoted by $Q_{i}$ prior to the current queue getting scheduled, it won't get scheduled until the current queue, its subsequent queues and the queues prior to $Q_{i}$ get scheduled.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% I/O %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Experimental Scheme}

On one hand, the input arguments to the proposed algorithm implementation are the number of processes to be scheduled, their burst time, their arrival time and the queue where each one belongs. On the other hand, output parameters are the average waiting time, average turnaround time and throughput. The following equations are used to calculate the previously mentioned output parameters:

\begin{equation}
    Average\; Waiting\; Time =  \frac{Total \; Waiting \; Time}{Number \; of \; Processes} \label{eq2}
\end{equation}

\begin{equation}
    Average\; Turnaround\; Time =  \frac{Total \; Turnaround \; Time}{Number \; of \; Processes} \label{eq3}
\end{equation}

\begin{equation}
    Throughput =  \frac{Number \; of \; Executed \; Processes}{Total \; Execution \; Time} \label{eq4}
\end{equation}

% \vspace{4mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PERFORMANCE METRICS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Performance Metrics}

As a means to have a concrete, viable evaluation of either the proposed algorithm or any other scheduling algorithm, the output parameters are taken into consideration for analysis. Since the average waiting time indicates the average time that a  process had to Starve for, therefore the lower the average waiting time is the better. The same principle applies to the average turnaround time and the number of context switches, as the former implies the average time spent by the process since its arrival time to its completion and the latter costs time as the CPU is assigned back and forth between different processes. Contrarily to the prior metrics, the larger the throughput is the better as it indicates the number of processes that are completely executed per unit time.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% SIMULATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Simulation}

For the sake of showcasing the proposed algorithm, a number of processes, their predetermined burst time values and their arrival time values are taken as input to the Python simulation script. Suppose that the input to the script is according to the following table:

\begin{table}[H]
    \caption{}
    \centering
     \begin{tabular}{||c c c c||} 
     \hline
     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
     \hline
     \hline
     1 & 0 & 60 & 1 \T \B \\ 
     \hline
     2 & 0 & 50 & 1 \T \B \\
     \hline
     3 & 0 & 40 & 2 \T \B \\
     \hline
     4 & 0 & 30 & 2 \T \B \\
     \hline
     5 & 0 & 10 & 3 \T \B \\ 
     \hline
     6 & 0 & 210 & 3 \T \B \\ 
     \hline
     7 & 0 & 200 & 3 \T \B \\ 
     \hline
     \end{tabular}
     \label{table1}
\end{table}

According to the proposed algorithm, the time quanta calculated are as follows:

\begin{table}[H]
    \caption{}
    \centering
     \begin{tabular}{||c c||} 
     \hline
     \textit{\textbf{Queue}} & \textit{\textbf{Quantum Value}} \T \B \\ 
     \hline
     \hline
     1 & 55 \T \B \\ 
     \hline
     2 & 40 \T \B \\
     \hline
     3 & 615 \T \B \\
     \hline
     4 & 0 \T \B \\
     \hline
     5 & 0 \T \B \\ 
     \hline
     \end{tabular}
\end{table}

All processes are sorted in ascending order according to their remaining time and are scheduled by assigning the time quantum calculated for their respective queue. The time spent scheduling a particular queue is the waiting time for its subsequent queues.

The scheduling process goes as follows:

\begin{figure}[H]
        \begin{center}
        \begin{tabular}{|c|c|}
         \hline
            $P_{2}$ & $P_{1}$\T\B\\ 
         \hline
        \end{tabular}
        \end{center}
        \begin{center}
            \begin{tabular}{c c c}
                   0 & 50 & 105\\ 
            \end{tabular}
        \end{center}
    \caption{$Q_{1}$ Gantt Chart}
\end{figure}

Considering that each process in $Q_{1}$ is assigned a quantum value of $50$, as we reach the last process in $Q_{1}$, the total time elapsed equals $105$, which happens to be the time that all the other processes in the subsequent queues had to wait for, hence the addition of their waiting time by a value of $105$ units of time.

\begin{figure}[H]
    \begin{center}
    \begin{tabular}{|c|c|c|c|}
     \hline
        $P_{1}$ & $P_{5}$ & $P_{4}$ & $P_{3}$\T\B\\ 
     \hline
    \end{tabular}
    \end{center}
    \begin{center}
        \begin{tabular}{c c c c c}
               105 & 110 & 120 & 150 & 190\\ 
        \end{tabular}
    \end{center}
\caption{$Q_{2}$ Gantt Chart}
\end{figure}

\begin{figure}[H]
    \begin{center}
    \begin{tabular}{|c|c|}
     \hline
        P7 & P6\T\B\\ 
     \hline
    \end{tabular}
    \end{center}
    \begin{center}
        \begin{tabular}{c c c}
               190 & 390 & 600\\ 
        \end{tabular}
    \end{center}
\caption{$Q_{3}$ Gantt Chart}
\end{figure}

Whenever processes reach the lowest queue precompletion, they are scheduled using the RR scheduling algorithm with a relatively large quantum time value which is in most cases similar to using the FCFS algorithm because, as the time quantum value of an RR algorithm tends to infinity which could practically be a very large number relative to the available processes remaining time values, the algorithm tends to morph into the FCFS algorithm. This procedure is iterated until all the processes are finished. Simulation results are shown in the table below:

\begin{table}[H]
    \caption{}
    \centering
     \begin{tabular}{||c c c||} 
     \hline
     \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}} & \textit{\textbf{Throughput}}\T \B \\ 
     \hline
     \hline
     230 & 144.3 & 0.011667 \T \B \\ 
     \hline
     \end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% COMPARISONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

To assess the performance of the proposed algorithm implementation, multiple test cases are addressed and analyzed in seven different experiments. In each experiment, the output of the proposed algorithm implementation is compared to the output of another scheduling algorithm implementation addressed in a different paper, such as standard MLFQ algorithm with static quantum RR and other variants of MLFQ algorithms and RR algorithms.

In this experiment, the proposed algorithm is compared against two MLFQ algorithm variants stated in {b4}. The first uses a static version of the RR algorithm for scheduling each queue, while the second variant uses a dynamic version of the RR algorithm for doing so.

\begin{table}[H]
    \caption{Experiment 1 Input}
    \centering
     \begin{tabular}{||c c c c||} 
     \hline
     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
     \hline
     \hline
     1 & 1 & 25 & 1 \T \B \\ 
     \hline
     2 & 5 & 70 & 1 \T \B \\
     \hline
     3 & 6 & 84 & 1 \T \B \\
     \hline
     4 & 7 & 17 & 1 \T \B \\
     \hline
     5 & 8 & 35 & 1 \T \B \\ 
     \hline
     \end{tabular}
\end{table}

\begin{table}[H]
    \caption{Experiment 1 Results}
    \centering
    \begin{tabular}{||c c c||}
        \hline
        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
    \hline
    \hline
    \textbf{Proposed Algorithm} & 115 & 68.8 \T \B\\ \hline
    \textbf{Dynamic RR MLFQ} & 150.8 & 107.6\T \B\\ \hline
    \textbf{Static RR MLFQ} & 161.4 & 116.2 \T \B\\ \hline
     \end{tabular}
\end{table}

\subsubsection{Experiment 2}

In this experiment, the proposed algorithm is compared against two MLFQ algorithm variants stated in {b4}. The first uses a static version of the SJFRR algorithm for scheduling each queue, while the second variant uses a dynamic version of the SJFRR algorithm for doing so.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{pgfplots}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{float}
\usepackage{adjustbox}

@@

\title{Improved Global Routing By Using A-Star Algorithm\\}

@@

\medskip
\par
In \cite{b13} they proposed an approach to not only perform pathfinding, but also the global routers are also required to generate a set of connected rectangle guides,  each of which contains an integral number of G-cells so that the detailed router can find a path within the guides to connect all pins of each net and reduce a given cost function to the minimum. \\
The proposed 3D pattern routing generates 3D topologies directly, while the traditional 3D pattern routing only generates 2D topologies and uses an extra layer for the assignment level. They, therefore, proposed a combination of 2D pattern routing with layer assignment and used it to choose a path for each two-pin net, and, with the help of dynamic programming, they ensure that an optimal solution can be found if it exists.
The overall flow of their proposed algorithm can be divided into 3 parts, summarized as follows:
\begin{enumerate}
	\item Initial routing:
    \begin{enumerate}
    	\item Pattern Routing Planning: \\
        In order to carry out 3D pattern routing, each multi-pin net first will be broken into set of two pin nets in this step.        
        \item 3D Pattern Routing with Layer Assignment: \\
        After breaking down the nets into two-pin nets and decide their order,
        pattern routing and layer assignment are performed simultaneously using a dynamic programming algorithm.
        Rather than performing layer assignment after a net is a pattern routed,
        our dynamic programming algorithm merges the two steps to minimize the overall cost
        and Prevent loss of precision caused by compressing the 3D grid graph to 2D.
    \end{enumerate}
    \item Multi-level 3D Maze Routing: \\
    After initial routing, the nets with violations will be destroyed and multiple iterations of rip-up and reroute (RRR) may be performed by maze routing. The multi-level 3D Maze Routing is repeated until there's no overflow. Because the maze routing on the entire 3d  graph would take too much time because of the wide search space, an algorithm that limits the search area to the bounding box of the net will make rerouting much faster, but it may reduce the routing quality.
    Considering the above, the proposed algorithm Uses multi-level 3d maze routing to allow graph searching process while reaching reasonable trade off between time and routing quality.
    The proposed routing technique has two levels, each serves a different purpose:
    \begin{enumerate}
    	\item  Maze Routing Planning (Bounding Box Generation): \\
        In order to carry out 3D pattern routing, each multi-pin net will first be broken down into a set of two-pin nets in this step.        
        \item 3D Maze Routing within Bounding Box (fine-grained maze routing within guides): \\
        Performs another level of maze routing, it seeks to find a path with the minimum
        actual cost within the search space.
    \end{enumerate}
	\item Route guide generation \& patching: \\
    The output of the global router is connected rectangular route guides, the algorithm proposes a new technique called patching to add some stand-alone route guides or patches onto the routed path to further improve the detailed routing.
\end{enumerate}

They introduce a global 3D router that could enhance the routing well in efficiency and quality. The 3d routing technique combines 2d routing and assignment of layers and helps most nets to be routed quickly and optimally. A patching method that actually contributes to useful route guidance to improve detailed routing in some way. An innovative probability-based cost scheme which takes into account the risk of overflow, the total wire length, and it is also capable of reducing the number of via and the total wire length while avoiding overflow and preserving enough edge capacity which is the number of paths that can pass through the edge. A multi-level maze routing method which is used to shrink the search space and then performs a bounded maze routing to find a minimum cost path.in that method we decided to work on the time parameter by instead of using the Dijkstra algorithm we will use the A-Star algorithm with a proposed heuristic function that will improve the time.

@@

    \foreach \x in {0,0.5,...,3.5}{
        \foreach \y in {0,0.5,...,2}
            \node[box] at (\x,\y){};
    }
    \node [box,fill=orange] at (0.5,1){S};
    \node[box,fill=orange  ] at (3,1){D};
    \node [box,fill=orange] at (0.5,1.5){};  
    \node [box,fill=orange] at (1,1.5){};  
    \node [box,fill=orange] at (1.5,1.5){};
    \node [box,fill=orange] at (2,1.5){};
    \node [box,fill=orange] at (2.5,1.5){};
    \node [box,fill=orange] at (3,1.5){};
    \node [box,fill=cyan] at (0,1){};
    \node [box,fill=cyan] at (1,1){};
    \node [box,fill=cyan] at (1.5,1){};
    \node[box,fill=black  ] at (2,1){ };  
    \end{tikzpicture}
}
\caption{Comparison between Dijkstra \& A-Star }
\label{fig:GlobalRoutingProcess}
\end{figure}
\medskip
In the illustrative example the visited nodes are marked in cyan color, the path is in orange color, and the blocked cells are black.
Both have path of six cells which in our case they have optimal wire length but totally different running time as Dijkstra visits much more nodes than A-Star
, in the case of many target nodes, Dijkstra might be better in total wire length but much slower than A-Star, with an appropriate heuristic function we can minimize the time and try to reach optimal wire length. The heuristic function is a way of informing the search about the path to a target that provides an intelligent way of guessing which neighbor of the node is going to lead to the target faster. Hence, our heuristic function composed of Manhattan distance, layer index, and some constants.
\begin{multline*}
    h = \ln (\mid p1 \cdot x-p2 \cdot x\mid+\mid p1 \cdot y-p2 \cdot y\mid)*const1 \\ 
     +(\mid p1 \cdot layerid-p2 \cdot layerid\mid)*const2 \\
\end{multline*}
The global router is implemented using C++ with the boost library, and a parser for LEF/DEF formats. We conducted our experiment with the same configuration and tried to test the global router behavior using A-Star algorithm instead of Dijkstra's.

@@

\subsection{Proposed Algorithm}
% \floatstyle{norules}
\restylefloat{algorithm}
\begin{algorithm}[H]
    \caption{A-Star Algorithm}
    \hspace*{\algorithmicindent} \textbf{Input:} Grid values $g$, Source $s$, Destination $d$\\
    \hspace*{\algorithmicindent} \textbf{Output:} Path\\
    \begin{algorithmic}[1]
    \Procedure {A-Star}{}
    % Return  Average waiting time, throughput
    \Statex Declaration and Initialisation:
    \State Cells $\theta$ % The Cells in the grid.
    \State Visited Nodes $\phi$ % Nodes already visited.
    \State Openlist Nodes $\delta$ % Nodes still to be visited. pq
    \State The cost from Starting point to a given node $g$
    \State The heuristic function $h$
    \State (The cost of $g$ + The cost of $h$) is $f$
    \If{$s$ or $d$ is invalid}
        \Return
    \EndIf
    \If{$s$ or $d$ is blocked}
        \State \Return
    \EndIf
    \If{$s$ = $d$}
        \State \Return
    \EndIf
    \State Initialize $\delta$ 
    \State Initialize $\phi$
        \While{$\delta$ is not empty}
            \State $currNode$  = node with least $f$ in $\delta$
            \State $\delta$.Remove($currNode$)
            \State Generate 4 neighbours of $currNode$
            \For{$neighbour \in neighbours$}
            \If{$neighbour$ = $d$}
                \State Get path
                \State \Return
            \ElsIf{$neighbour \notin \phi$ and $neighbour$ is not blocked}
                \State $gnew$ = $currNode$.$g$ + distance between neighbour and currNode
                \State $hnew$ = distance from $d$ to $neighbour$
                \State $fnew$ = $gnew$ + $hnew$
                \If{$fnew < neighbour$.$f$}
                \State $neighbour$.$g$ = $currNode$.$g$ + distance between neighbour and currNode
                \State $neighbour$.$h$ = distance from $d$ to $neighbour$
                \State $neighbour$.$f$ = $neighbour$.$g$ + $neighbour$.$h$
                \State $\delta$.Add($neighbour$)
                \EndIf
            \EndIf
            \EndFor
        \State $\phi$.Add($currNode$)
        \EndWhile
        \EndProcedure
    \end{algorithmic}
\end{algorithm}

@@

we implement global routing with A-Star router algorithm in c++ language
with Rsyn to parse input test cases files with format LEF/DEF. All
experiments are performed on a Machine with 2 GHZ Intel Processor
and 8 GB RAM. our algorithm is focus on three important factors :total
wire-length, channel congestion ,number of vias. Our target is to
minimize a convex combination of the total wire-length and the number
of vias that represent the bends in the tree that result in solving
the net of pins to be connected.our test cases input are all from
ICCAD'19 contest for global routing.we test our code with different
heuristic functions -that affect the run time of A-Star- to check its
effect on CPU run time.our concern is on wire-length and number of
vias result from routing without increasing in-feasibility.we generate
the trees of all nets in parallel to reduce running by using multi-threaded
approach to generate the net results tree as this step has the most
costly part of the router algorithm.our algorithm not only route each net to find a path that connect all pins of the net, but it also generate a set of connected rectangle for each net to be used in detailed routing and to minimize its cost.

In this experiment we compare run time of router with Dijkstra Router
and out A-Star router with heuristic function with different constants
of heuristic functions that affect the run time of the router.heuristic
function help us to know how near the point to the target point so it help in decreasing the cost of routing:

\begin{multline*}
h1=(\mid p1\cdot x-p2\cdot x\mid+\mid p1\cdot y-p2\cdot y\mid)*const1\\
+(\mid p1\cdot layerid-p2\cdot layerid\mid)*const2\\
\end{multline*}

\begin{multline*}
h2=ln(\mid p1\cdot x-p2\cdot x\mid+\mid p1\cdot y-p2\cdot y\mid)*const1\\
+(\mid p1\cdot layerid-p2\cdot layerid\mid)*const2\\
\end{multline*}

\begin{multline*}
h3=(\mid p1\cdot x-p2\cdot x\mid+\mid p1\cdot y-p2\cdot y\mid)*const1\\
+ln(\mid p1\cdot layerid-p2\cdot layerid\mid)*const2\\
\end{multline*}

{\tiny{}}
\begin{table}[b]
{\tiny{}\caption{\label{tab:Compare-run-time}Compare run time of Dijkstra router and
A-Star router with Heuristic-Function 1}
}{\tiny\par}
\centering{}{\footnotesize{}}%
\begin{adjustbox}{width=\columnwidth,center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
\multirow{2}{*}{{\footnotesize{}Design}} & \multicolumn{4}{c|}{{\footnotesize{}A-Star}} & \multirow{2}{*}{{\footnotesize{}Dijkstra}}\tabularnewline
\cline{2-5} \cline{3-5} \cline{4-5} \cline{5-5} 
 & {\footnotesize{}(0.2,0.1)} & {\footnotesize{}(0.3,0.3)} & {\footnotesize{}(0.5,0.5)} & \multicolumn{1}{c||}{{\footnotesize{}(0.5,0.5)}} & \tabularnewline
\hline 
\hline 
{\footnotesize{}test1} & {\footnotesize{}75.843764} & {\footnotesize{}87.797614} & {\footnotesize{}87.086193} & {\footnotesize{}96.377979} & {\footnotesize{}91.348007}\tabularnewline
\hline 
{\footnotesize{}test2} & {\footnotesize{}2.511599} & {\footnotesize{}2.606054} & {\footnotesize{}2.874605} & {\footnotesize{}2.497377} & {\footnotesize{}3.435606}\tabularnewline
\hline 
{\footnotesize{}test3} & {\footnotesize{}12.381436} & {\footnotesize{}14.959666} & {\footnotesize{}14.859677} & {\footnotesize{}14.766495} & {\footnotesize{}11.824573}\tabularnewline
\hline 
{\footnotesize{}test4} & {\footnotesize{}0.075472} & {\footnotesize{}0.073069} & {\footnotesize{}0.073769} & {\footnotesize{}0.072691} & {\footnotesize{}0.071829}\tabularnewline
\hline 
{\footnotesize{}test5} & {\footnotesize{}0.073988} & {\footnotesize{}0.072911} & {\footnotesize{}0.074165} & {\footnotesize{}0.072767} & {\footnotesize{}0.071945}\tabularnewline
\hline 
{\footnotesize{}test6} & {\footnotesize{}6.948016} & {\footnotesize{}6.266789} & {\footnotesize{}5.198969} & {\footnotesize{}6.906992} & {\footnotesize{}7.0385}\tabularnewline
\hline 
\end{tabular}{\footnotesize\par}
\end{adjustbox}
\end{table}
{\tiny\par}

\begin{table}
\caption{\label{tab:Compare-run-time-1}Compare run time of Dijkstra router
and A-Star router with Heuristic-Function 2}

\centering{}{\footnotesize{}}%
\begin{adjustbox}{width=\columnwidth,center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
\multirow{2}{*}{{\footnotesize{}Design}} & \multicolumn{4}{c|}{{\footnotesize{}A-Star}} & \multirow{2}{*}{{\footnotesize{}Dijkstra}}\tabularnewline
\cline{2-5} \cline{3-5} \cline{4-5} \cline{5-5} 
 & {\footnotesize{}(0.1,0.1)} & {\footnotesize{}(0.2,0.1)} & {\footnotesize{}(0.3,0.3)} & {\footnotesize{}(0.5,0.5)} & \tabularnewline
\hline 
\hline 
{\footnotesize{}test1} & {\footnotesize{}90.440165} & {\footnotesize{}93.288501} & {\footnotesize{}89.414646} & {\footnotesize{}96.377979} & {\footnotesize{}91.348007}\tabularnewline
\hline 
{\footnotesize{}test2} & {\footnotesize{}2.461400} & {\footnotesize{}2.469304} & {\footnotesize{}2.480592} & {\footnotesize{}2.497377} & {\footnotesize{}3.435606}\tabularnewline
\hline 
{\footnotesize{}test3} & {\footnotesize{}12.264829} & {\footnotesize{}13.449206} & {\footnotesize{}12.039944} & {\footnotesize{}14.766495} & {\footnotesize{}11.824573}\tabularnewline
\hline 
{\footnotesize{}test4} & {\footnotesize{}0.071577} & {\footnotesize{}0.157244} & {\footnotesize{}0.078624} & {\footnotesize{}0.072691} & {\footnotesize{}0.071829}\tabularnewline
\hline 
{\footnotesize{}test5} & {\footnotesize{}0.078316} & {\footnotesize{}0.090906} & {\footnotesize{}0.071333} & {\footnotesize{}0.072767} & {\footnotesize{}0.071945}\tabularnewline
\hline 
{\footnotesize{}test6} & {\footnotesize{}6.893310} & {\footnotesize{}6.400888} & {\footnotesize{}6.974920} & {\footnotesize{}6.906992} & {\footnotesize{}7.038505}\tabularnewline
\hline 
\end{tabular}{\footnotesize\par}
\end{adjustbox}
\end{table}

\begin{table}
{\tiny{}\caption{\label{tab:Continue-compare-run} compare run time of Dijkstra router
and A-Star router with Heuristic-Function 3}
}{\tiny\par}
\centering{}{\footnotesize{}}%
\begin{adjustbox}{width=\columnwidth,center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
\multirow{2}{*}{{\footnotesize{}Design}} & \multicolumn{4}{c|}{{\footnotesize{}A-Star}} & \multirow{2}{*}{{\footnotesize{}Dijkstra}}\tabularnewline
\cline{2-5} \cline{3-5} \cline{4-5} \cline{5-5} 
 & {\footnotesize{}(0.1,0.1)} & {\footnotesize{}(0.2,0.1)} & {\footnotesize{}(0.3,0.3)} & {\footnotesize{}(0.5,0.5)} & \tabularnewline
\hline 
\hline 
{\footnotesize{}test1} & {\footnotesize{}86.598509} & {\footnotesize{}83.204272} & {\footnotesize{}103.166426} & {\footnotesize{}102.378304} & {\footnotesize{}91.348007}\tabularnewline
\hline 
{\footnotesize{}test2} & {\footnotesize{}2.481847} & {\footnotesize{}2.486656} & {\footnotesize{}3.622759} & {\footnotesize{}2.556863} & {\footnotesize{}3.435606}\tabularnewline
\hline 
{\footnotesize{}test3} & {\footnotesize{}12.655603} & {\footnotesize{}15.447421} & {\footnotesize{}15.629251} & {\footnotesize{}20.004493} & {\footnotesize{}11.824573}\tabularnewline
\hline 
{\footnotesize{}test4} & {\footnotesize{}0.073731} & {\footnotesize{}0.070911} & {\footnotesize{}0.073468} & {\footnotesize{}0.103421} & {\footnotesize{}0.071829}\tabularnewline
\hline 
{\footnotesize{}test5} & {\footnotesize{}0.078171} & {\footnotesize{}0.079362} & {\footnotesize{}0.088107} & {\footnotesize{}0.099699} & {\footnotesize{}0.071945}\tabularnewline
\hline 
{\footnotesize{}test6} & {\footnotesize{}6.470339} & {\footnotesize{}7.195767} & {\footnotesize{}8.455288} & {\footnotesize{}7.637577} & {\footnotesize{}7.038505}\tabularnewline
\hline 
\end{tabular}{\footnotesize\par}
\end{adjustbox}
\end{table}

we notice from Table\ref{tab:Compare-run-time},Table\ref{tab:Continue-compare-run},Table\ref{tab:Compare-run-time-1}
that heuristic function affect the running time of router ,decreases
it to be lower than Dijkstra router's running time in many test cases.
the running time changes with the change of heuristic function constants.
we notice that higher constants increase the running time and sometimes
be greater than Dijkstra router's run time. Heuristic function 2 has
overall results which is better than others, with using more efficient
heuristic functions,run time and wire-length and vias number combination
may improve greatly.

@@

we used ISPD19 benchmarks to compare out results with another global
routing algorithms such as TripleZ and NTUidRoute. we compare the
results in terms of total wire length score and vias score. we compare
results of our algorithm which focus on factors - total wire-length,number
of vias in the routing results - with TripleZ and NTUidRoute algorithms
in ICCAD'19 Table\ref{tab:compared-Wire-Lengh},Table \ref{tab:compared-Vias}
.we use multi-threaded approach to generate net result trees in parallel
so we have done our experiments using 8 threads in all test cases.
score used as unit to compare ,score of wire length is a function
of metal pitch and wire length and weight:

\[
WLScore=\frac{wire-length*weight}{metal-pitch}
\]

score of vias is function of number of vias :

\[
ViasScore=\#vias*2
\]
